---
title: "VNet Data Henry"
output: html_document
highlight: Pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Week 2

## Data

### To Do

#### Different types of activity

- Website openings
  - Websites with auto-refresh (Facebook, Gmail, ec.)
  - Static websites (Formel1.de)
  - Websites with lots of articles, pictures from other sources (bbc)
- Websockets (google docs)
- Mail client refreshing and static activity
- Update scan (for what update exactly??)
- Time synchronisation (already got that one)
- Services like Onedrive, google drive
- Microsoft Office? Word, Excel, OneNote (which syncs all the time), Calendar app
- Spotify? Streaming
- Skype (see paper)
- Network discovery (Heartbeat discovery)



## Saturday 19.05.

#### Start-up and stand-by with time synchronisation

- 12:26:10 Start up of Kali-Linux
- 12:28:35 Log-in
- 12:35:00 turn off time synch

```{bash, eval=FALSE}
timedatectl set-ntp 0
```

- 13:05:00 turn on time synch
```{bash, eval=FALSE}
timedatectl set-ntp 1
```

- 14:33:30 turn off time synch
```{bash, eval=FALSE}
timedatectl set-ntp 0
```

#### Google docs

It didn't have a name until now. I'll call it "no-polling," to contrast with polling and long-polling.

With polling, the client periodically sends queries for new data.

With long-polling, the client queries for data, and the server holds onto the request, ending the response with the updates when there are updates.

No-polling (what Google Drive does) takes advantage of how the browser can read data from the body of a request before the request is complete. So as collaborators do more typing and edits, the server appends more data to the current request. If certain limits are met (length of the content or duration of the request), the request completes, and the client initiates a new request with the server.

- 14:38 open browser, go to google docs, log-in etc.

- 14:41:00 open browser 
- 14:42:00 open google docs
- 14:43:00 edit a little in the doc
- 14:44:00 close browser
- 14:57:00 shutdown Kali Linux

```{r Initial,eval=TRUE,cache=FALSE,echo=FALSE, results=FALSE}
setwd("~/Desktop/Project/VNet/Data/")

Flows <- Outflows <- read.table("nf_0519.txt",sep=",",header=FALSE, stringsAsFactors = FALSE,skip=1,fill=TRUE)
del <- nrow(Flows)

Flows <- Flows <- read.table("nf_0519.txt",sep=",",header=FALSE, stringsAsFactors = FALSE,skip=1,nrows=del-4,fill=TRUE)
t11 <- sapply(strsplit(Flows[,1]," "), "[",2)
Flows[,1] <- c(data.matrix(read.table(text=t11,sep=":"))%*%c(3600,60,1))
Flows[,5] <- sapply(strsplit(Flows[,5],":"), "[",2)
Flows[,7] <- sapply(strsplit(Flows[,7],":"), "[",2)
Flows[,3] <- trimws(Flows[,3],which="both")
Flows[,4] <- trimws(Flows[,4],which="both")
Flows[,5] <- trimws(Flows[,5],which="both")
Flows[,6] <- trimws(Flows[,6],which="both")
Flows[,7] <- trimws(Flows[,7],which="both")
Flows[,9] <- trimws(Flows[,9],which="both")
Flows[,8] <- gsub(" M","000000",Flows[,8])
Flows[,9] <- gsub(" M","000000",Flows[,9])
Flows[,8] <- gsub(" G","000000000",Flows[,8])
Flows[,9] <- gsub(" G","000000000",Flows[,9])

colnames(Flows) <- c("timeStamp","duration","proto","srcip","srcport",
                              "destip","destport","packetcount","bytes","flowcount")
Flows <- Flows[order(Flows[,1]),]


Outflows <- Flows[Flows[,4]=="192.168.1.100",]
Inflows <- Flows[Flows[,6]=="192.168.1.100",]
Others <- Flows[Flows[,6]!="192.168.1.100"&Flows[,4]!="192.168.1.100",]

# dim(Inflows)
# dim(Outflows)


# Outflows <- Outflows[Outflows[,1]/3600>13.99,]
# Outflows[,1] <- Outflows[,1]-min(Outflows[,1])
# Inflows <- Inflows[Inflows[,1]/3600>13.99,]
# Inflows[,1] <- Inflows[,1]-min(Inflows[,1])


#Outflows ###############################################################

Outflows_b <- Outflows
Inflows_b <- Inflows

Outflows_b[,8] <- as.numeric(Outflows_b[,8])
Outflows_b[,9] <- as.numeric(Outflows_b[,9])
Inflows_b[,8] <- as.numeric(Inflows_b[,8])
Inflows_b[,9] <- as.numeric(Inflows_b[,9])

#Colors and groups
coldout <- rep("black",dim(Outflows)[1])
coldin <- rep("black",dim(Inflows)[1])
colpout <- rep("black",dim(Outflows)[1])
colpin <- rep("black",dim(Inflows)[1])
colbout <- rep("black",dim(Outflows)[1])
colbin <- rep("black",dim(Inflows)[1])

quantile(as.numeric(Outflows[,2]),probs = c(0.7,0.95,0.99,0.999))
quantile(as.numeric(Inflows[,2]),probs = c(0.7,0.95,0.99,0.999))
durationsv <- c(-1,0,1,10,100,600,Inf)
cold <- c("black","black","darkred","red","purple","green")

for(i in 2:length(durationsv)){
  Outflows[Outflows_b[,2]>durationsv[i-1]&Outflows_b[,2]<=durationsv[i],2] <- paste("<",durationsv[i])
  coldout[Outflows_b[,2]>durationsv[i-1]&Outflows_b[,2]<=durationsv[i]] <- cold[i-1]
  Inflows[Inflows_b[,2]>durationsv[i-1]&Inflows_b[,2]<=durationsv[i],2] <- paste("<",durationsv[i])
  coldin[Inflows_b[,2]>durationsv[i-1]&Inflows_b[,2]<=durationsv[i]] <- cold[i-1]
}

quantile(as.numeric(Outflows[,8]),probs = c(0.7,0.95,0.99,0.999))
quantile(as.numeric(Inflows[,8]),probs = c(0.7,0.95,0.99,0.999))
paketsv <- c(-1,1,10,100,1000,10000,100000,Inf)
colp <- c("black","black","darkred","red","purple","purple","green")

for(i in 2:length(paketsv)){
  Outflows[Outflows_b[,8]>paketsv[i-1]&Outflows_b[,8]<=paketsv[i],8] <- paste("<",paketsv[i])
  colpout[Outflows_b[,8]>paketsv[i-1]&Outflows_b[,8]<=paketsv[i]] <- colp[i-1]
  Inflows[Inflows_b[,8]>paketsv[i-1]&Inflows_b[,8]<=paketsv[i],8] <- paste("<",paketsv[i])
  colpin[Inflows_b[,8]>paketsv[i-1]&Inflows_b[,8]<=paketsv[i]] <- colp[i-1]
}

#quantile(as.numeric(Outflows[,9]),probs = c(0.7,0.95,0.99,0.999))
#quantile(as.numeric(Inflows[,9]),probs = c(0.7,0.95,0.99,0.999))
bytesv <- c(-1,100,10000,1000000,100000000,1000000000,Inf)
colb <- c("black","darkred","red","purple","purple","green")

for(i in 2:length(paketsv)){
  Outflows[Outflows_b[,9]>bytesv[i-1]&Outflows_b[,9]<=bytesv[i],9] <- paste("<",bytesv[i])
  colbout[Outflows_b[,9]>bytesv[i-1]&Outflows_b[,9]<=bytesv[i]] <- colb[i-1]
  Inflows[Inflows_b[,9]>bytesv[i-1]&Inflows_b[,9]<=bytesv[i],9] <- paste("<",bytesv[i])
  colbin[Inflows_b[,9]>bytesv[i-1]&Inflows_b[,9]<=bytesv[i]] <- colb[i-1]
}


library(RColorBrewer)
n <- 74
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
#pie(rep(1,n), col=sample(col_vector, n))
```

```{r Plots 19.05.,eval=TRUE,cache=FALSE,fig.height=50,fig.width=15,echo=FALSE}
window <- c(0,130)+52676.02

yax <- seq(from = window[1], to = window[2], by = 5)

par(mfrow=c(1,2))


nout <- sum(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6])>2)
nin <- sum(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4])>2)

IPout <- names(sort(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]),decreasing = TRUE))
IPin <- names(sort(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]),decreasing = TRUE))

colsout <- rep("black",length(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]))
colsin <- rep("black",length(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],6]))

for(i in 1:nout){
  colsout[Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]==IPout[i]]=col_vector[i]
}

for(i in 1:nin){
  colsin[Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]==IPin[i]]=col_vector[i]
}

outUDP <- Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],3]=="UDP"
outTCP <- Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],3]=="TCP"
inUDP <- Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],3]=="UDP"
inTCP <- Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],3]=="TCP"



#sort(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]),decreasing = TRUE)
#sort(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]),decreasing = TRUE)

#Outflows ##################

plot(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0,Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     col=colsout[outUDP],ylim=rev(window),pch=16,cex=0.8,xlim=c(-0.6,0.5),axes=FALSE,frame.plot=TRUE,
     main="Outflows 1: Go to google.com",ylab=" " ,xlab=" ")
axis(side = 2, at = yax)
points(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.5,Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
       col=colsout[outTCP],cex=0.8,pch=16)

#Ports
text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.07, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],7],offset = 0, cex = 0.7)
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.43, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],7],offset = 0, cex = 0.7)

#Duration

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.16, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.34, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Bytes

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.3, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.2, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Pakets

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.4, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.1, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Inflows ##################

plot(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0,Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     col=colsin[inUDP],ylim=rev(window),pch=16,cex=0.8,xlim=c(-0.6,0.5),axes=FALSE,frame.plot=TRUE,
     main="Outflows 1: Go to google.com",ylab=" " ,xlab=" ")
axis(side = 2, at = yax)
points(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.5,Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
       col=colsin[inTCP],cex=0.8,pch=16)

#Ports
text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.07, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],5],offset = 0, cex = 0.7)
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.43, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],5],offset = 0, cex = 0.7)

#Duration

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.16, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.34, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

#Bytes

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.3, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.2, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

#Pakets

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.4, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.1, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])


```
