---
title: "VNet Data Henry"
output: html_document
highlight: Pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Week 2

## Data

### To Do
What I did so far:


10.05.

- 13:44   ping 8.8.8.8 (49440s)
  8 packages sent
- 13:45   go to google.com (49500s)
- 13:46  go to https://www.youtube.com/watch?v=J0tGubH9ZyM (49560s)
- 13:46 do nothing for a few minutes to check background traffic of kali linux (everything closed)
- 13:50   nmap -sP 192.168.0.0-100  (49800s)
- 13:51   nmap -sV 192.168.1.1 -A  (49860s)
- 13:54   open file:///usr/share/kali-defaults/web/homepage.html (50040s)
- 13:55   open facebook.com --> https://www.facebook.com/ (not logged in) (50100s)
- 13:56   go to bbc.com  (50160s)
- 13:56   go to google.com (with bbc still open)
- 13:57   close google.com  (50220s)
- 13:57 close bbc.com


# Looking at the data:
```{r Initial,eval=TRUE,cache=FALSE,echo=FALSE, results=FALSE}
setwd("~/Desktop/VNet/Data/")

Flows <- Outflows <- read.table("nf_data.txt",sep=",",header=FALSE, stringsAsFactors = FALSE,skip=1,fill=TRUE)
del <- nrow(Flows)

Flows <- Flows <- read.table("nf_data.txt",sep=",",header=FALSE, stringsAsFactors = FALSE,skip=1,nrows=del-4,fill=TRUE)
t11 <- sapply(strsplit(Flows[,1]," "), "[",2)
Flows[,1] <- c(data.matrix(read.table(text=t11,sep=":"))%*%c(3600,60,1))
Flows[,5] <- sapply(strsplit(Flows[,5],":"), "[",2)
Flows[,7] <- sapply(strsplit(Flows[,7],":"), "[",2)
Flows[,3] <- trimws(Flows[,3],which="both")
Flows[,4] <- trimws(Flows[,4],which="both")
Flows[,5] <- trimws(Flows[,5],which="both")
Flows[,6] <- trimws(Flows[,6],which="both")
Flows[,7] <- trimws(Flows[,7],which="both")
Flows[,9] <- trimws(Flows[,9],which="both")
Flows[,8] <- gsub(" M","000000",Flows[,8])
Flows[,9] <- gsub(" M","000000",Flows[,9])
Flows[,8] <- gsub(" G","000000000",Flows[,8])
Flows[,9] <- gsub(" G","000000000",Flows[,9])

colnames(Flows) <- c("timeStamp","duration","proto","srcip","srcport",
                              "destip","destport","packetcount","bytes","flowcount")
Flows <- Flows[order(Flows[,1]),]


Outflows <- Flows[Flows[,4]=="192.168.1.100",]
Inflows <- Flows[Flows[,6]=="192.168.1.100",]
Others <- Flows[Flows[,6]!="192.168.1.100"&Flows[,4]!="192.168.1.100",]

#dim(Inflows)
#dim(Outflows)


# Outflows <- Outflows[Outflows[,1]/3600>13.99,]
# Outflows[,1] <- Outflows[,1]-min(Outflows[,1])
# Inflows <- Inflows[Inflows[,1]/3600>13.99,]
# Inflows[,1] <- Inflows[,1]-min(Inflows[,1])


#Outflows ###############################################################

Outflows_b <- Outflows
Inflows_b <- Inflows

Outflows_b[,8] <- as.numeric(Outflows_b[,8])
Outflows_b[,9] <- as.numeric(Outflows_b[,9])
Inflows_b[,8] <- as.numeric(Inflows_b[,8])
Inflows_b[,9] <- as.numeric(Inflows_b[,9])

#Colors and groups
coldout <- rep("black",dim(Outflows)[1])
coldin <- rep("black",dim(Inflows)[1])
colpout <- rep("black",dim(Outflows)[1])
colpin <- rep("black",dim(Inflows)[1])
colbout <- rep("black",dim(Outflows)[1])
colbin <- rep("black",dim(Inflows)[1])

quantile(as.numeric(Outflows[,2]),probs = c(0.7,0.95,0.99,0.999))
quantile(as.numeric(Inflows[,2]),probs = c(0.7,0.95,0.99,0.999))
durationsv <- c(-1,0,1,10,100,600,Inf)
cold <- c("black","black","darkred","red","purple","green")

for(i in 2:length(durationsv)){
  Outflows[Outflows_b[,2]>durationsv[i-1]&Outflows_b[,2]<=durationsv[i],2] <- paste("<",durationsv[i])
  coldout[Outflows_b[,2]>durationsv[i-1]&Outflows_b[,2]<=durationsv[i]] <- cold[i-1]
  Inflows[Inflows_b[,2]>durationsv[i-1]&Inflows_b[,2]<=durationsv[i],2] <- paste("<",durationsv[i])
  coldin[Inflows_b[,2]>durationsv[i-1]&Inflows_b[,2]<=durationsv[i]] <- cold[i-1]
}

quantile(as.numeric(Outflows[,8]),probs = c(0.7,0.95,0.99,0.999))
quantile(as.numeric(Inflows[,8]),probs = c(0.7,0.95,0.99,0.999))
paketsv <- c(-1,1,10,100,1000,10000,100000,Inf)
colp <- c("black","black","darkred","red","purple","purple","green")

for(i in 2:length(paketsv)){
  Outflows[Outflows_b[,8]>paketsv[i-1]&Outflows_b[,8]<=paketsv[i],8] <- paste("<",paketsv[i])
  colpout[Outflows_b[,8]>paketsv[i-1]&Outflows_b[,8]<=paketsv[i]] <- colp[i-1]
  Inflows[Inflows_b[,8]>paketsv[i-1]&Inflows_b[,8]<=paketsv[i],8] <- paste("<",paketsv[i])
  colpin[Inflows_b[,8]>paketsv[i-1]&Inflows_b[,8]<=paketsv[i]] <- colp[i-1]
}

quantile(as.numeric(Outflows[,9]),probs = c(0.7,0.95,0.99,0.999))
quantile(as.numeric(Inflows[,9]),probs = c(0.7,0.95,0.99,0.999))
bytesv <- c(-1,100,10000,1000000,100000000,1000000000,Inf)
colb <- c("black","darkred","red","purple","purple","green")

for(i in 2:length(paketsv)){
  Outflows[Outflows_b[,9]>bytesv[i-1]&Outflows_b[,9]<=bytesv[i],9] <- paste("<",bytesv[i])
  colbout[Outflows_b[,9]>bytesv[i-1]&Outflows_b[,9]<=bytesv[i]] <- colb[i-1]
  Inflows[Inflows_b[,9]>bytesv[i-1]&Inflows_b[,9]<=bytesv[i],9] <- paste("<",bytesv[i])
  colbin[Inflows_b[,9]>bytesv[i-1]&Inflows_b[,9]<=bytesv[i]] <- colb[i-1]
}


library(RColorBrewer)
n <- 74
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
#pie(rep(1,n), col=sample(col_vector, n))
```



```{r Facebook,eval=TRUE,cache=FALSE,fig.height=10,fig.width=15,echo=FALSE}
window <- c(0,30)+49530


yax <- seq(from = window[1], to = window[2], by = 5)

par(mfrow=c(1,2))


nout <- sum(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6])>2)
nin <- sum(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4])>2)

IPout <- names(sort(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]),decreasing = TRUE))
IPin <- names(sort(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]),decreasing = TRUE))

colsout <- rep("black",length(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]))
colsin <- rep("black",length(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],6]))

for(i in 1:nout){
  colsout[Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]==IPout[i]]=col_vector[i]
}

for(i in 1:nin){
  colsin[Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]==IPin[i]]=col_vector[i]
}

outUDP <- Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],3]=="UDP"
outTCP <- Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],3]=="TCP"
inUDP <- Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],3]=="UDP"
inTCP <- Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],3]=="TCP"



#sort(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]),decreasing = TRUE)
#sort(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]),decreasing = TRUE)

#Outflows ##################

plot(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0,Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     col=colsout[outUDP],ylim=rev(window),pch=16,cex=0.8,xlim=c(-0.6,0.5),axes=FALSE,frame.plot=TRUE,
     main="Outflows 1: Go to google.com",ylab=" " ,xlab=" ")
axis(side = 2, at = yax)
points(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.5,Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
       col=colsout[outTCP],cex=0.8,pch=16)

#Ports
text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.07, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],7],offset = 0, cex = 0.7)
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.43, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],7],offset = 0, cex = 0.7)

#Duration

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.16, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.34, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Bytes

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.3, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.2, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Pakets

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.4, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.1, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Inflows ##################

plot(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0,Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     col=colsin[inUDP],ylim=rev(window),pch=16,cex=0.8,xlim=c(-0.6,0.5),axes=FALSE,frame.plot=TRUE,
     main="Outflows 1: Go to google.com",ylab=" " ,xlab=" ")
axis(side = 2, at = yax)
points(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.5,Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
       col=colsin[inTCP],cex=0.8,pch=16)

#Ports
text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.07, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],5],offset = 0, cex = 0.7)
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.43, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],5],offset = 0, cex = 0.7)

#Duration

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.16, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.34, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

#Bytes

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.3, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.2, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

#Pakets

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.4, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.1, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

```


```{r youtube,eval=TRUE,cache=FALSE,fig.height=15,fig.width=15,echo=FALSE}
window <- c(0,40)+49560


yax <- seq(from = window[1], to = window[2], by = 5)

par(mfrow=c(1,2))


nout <- sum(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6])>2)
nin <- sum(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4])>2)

IPout <- names(sort(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]),decreasing = TRUE))
IPin <- names(sort(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]),decreasing = TRUE))

colsout <- rep("black",length(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]))
colsin <- rep("black",length(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],6]))

for(i in 1:nout){
  colsout[Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]==IPout[i]]=col_vector[i]
}

for(i in 1:nin){
  colsin[Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]==IPin[i]]=col_vector[i]
}

outUDP <- Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],3]=="UDP"
outTCP <- Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],3]=="TCP"
inUDP <- Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],3]=="UDP"
inTCP <- Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],3]=="TCP"



#sort(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]),decreasing = TRUE)
#sort(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]),decreasing = TRUE)

#Outflows ##################

plot(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0,Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     col=colsout[outUDP],ylim=rev(window),pch=16,cex=0.8,xlim=c(-0.6,0.5),axes=FALSE,frame.plot=TRUE,
     main="Outflows 2: View video on youtube (direct open)",ylab=" " ,xlab=" ")
axis(side = 2, at = yax)
points(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.5,Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
       col=colsout[outTCP],cex=0.8,pch=16)

#Ports
text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.07, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],7],offset = 0, cex = 0.7)
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.43, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],7],offset = 0, cex = 0.7)

#Duration

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.16, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.34, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Bytes

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.3, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.2, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Pakets

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.4, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.1, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Inflows ##################

plot(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0,Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     col=colsin[inUDP],ylim=rev(window),pch=16,cex=0.8,xlim=c(-0.6,0.5),axes=FALSE,frame.plot=TRUE,
     main="Inflows 2: View video on youtube (direct open)",ylab=" " ,xlab=" ")
axis(side = 2, at = yax)
points(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.5,Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
       col=colsin[inTCP],cex=0.8,pch=16)

#Ports
text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.07, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],5],offset = 0, cex = 0.7)
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.43, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],5],offset = 0, cex = 0.7)

#Duration

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.16, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.34, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

#Bytes

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.3, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.2, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

#Pakets

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.4, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.1, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

```

```{r portscan,eval=TRUE,cache=FALSE,fig.height=10,fig.width=15,echo=FALSE}
window <- c(0,30)+49890


yax <- seq(from = window[1], to = window[2], by = 5)

par(mfrow=c(1,2))


nout <- sum(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6])>2)
nin <- sum(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4])>2)

IPout <- names(sort(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]),decreasing = TRUE))
IPin <- names(sort(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]),decreasing = TRUE))

colsout <- rep("black",length(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]))
colsin <- rep("black",length(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],6]))

for(i in 1:nout){
  colsout[Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]==IPout[i]]=col_vector[i]
}

for(i in 1:nin){
  colsin[Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]==IPin[i]]=col_vector[i]
}

outUDP <- Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],3]=="UDP"
outTCP <- Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],3]=="TCP"
inUDP <- Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],3]=="UDP"
inTCP <- Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],3]=="TCP"



#sort(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]),decreasing = TRUE)
#sort(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]),decreasing = TRUE)

#Outflows ##################

plot(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0,Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     col=colsout[outUDP],ylim=rev(window),pch=16,cex=0.8,xlim=c(-0.6,0.5),axes=FALSE,frame.plot=TRUE,
     main="Outflows 3: Port scan",ylab=" " ,xlab=" ")
axis(side = 2, at = yax)
points(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.5,Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
       col=colsout[outTCP],cex=0.8,pch=16)

#Ports
text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.07, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],7],offset = 0, cex = 0.7)
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.43, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],7],offset = 0, cex = 0.7)

#Duration

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.16, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.34, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Bytes

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.3, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.2, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Pakets

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.4, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.1, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Inflows ##################

plot(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0,Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     col=colsin[inUDP],ylim=rev(window),pch=16,cex=0.8,xlim=c(-0.6,0.5),axes=FALSE,frame.plot=TRUE,
     main="Inflows 3: Port scan",ylab=" " ,xlab=" ")
axis(side = 2, at = yax)
points(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.5,Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
       col=colsin[inTCP],cex=0.8,pch=16)

#Ports
text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.07, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],5],offset = 0, cex = 0.7)
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.43, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],5],offset = 0, cex = 0.7)

#Duration

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.16, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.34, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

#Bytes

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.3, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.2, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

#Pakets

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.4, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.1, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

```


```{r bbc,eval=TRUE,cache=FALSE,fig.height=10,fig.width=15,echo=FALSE}
window <- c(0,30)+50160


yax <- seq(from = window[1], to = window[2], by = 5)

par(mfrow=c(1,2))


nout <- sum(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6])>2)
nin <- sum(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4])>2)

IPout <- names(sort(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]),decreasing = TRUE))
IPin <- names(sort(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]),decreasing = TRUE))

colsout <- rep("black",length(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]))
colsin <- rep("black",length(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],6]))

for(i in 1:nout){
  colsout[Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]==IPout[i]]=col_vector[i]
}

for(i in 1:nin){
  colsin[Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]==IPin[i]]=col_vector[i]
}

outUDP <- Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],3]=="UDP"
outTCP <- Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],3]=="TCP"
inUDP <- Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],3]=="UDP"
inTCP <- Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],3]=="TCP"



#sort(table(Outflows[Outflows[,1]>=window[1]&Outflows[,1]<=window[2],6]),decreasing = TRUE)
#sort(table(Inflows[Inflows[,1]>=window[1]&Inflows[,1]<=window[2],4]),decreasing = TRUE)

#Outflows ##################

plot(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0,Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     col=colsout[outUDP],ylim=rev(window),pch=16,cex=0.8,xlim=c(-0.6,0.5),axes=FALSE,frame.plot=TRUE,
     main="Outflows 4: BBC",ylab=" " ,xlab=" ")
axis(side = 2, at = yax)
points(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.5,Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
       col=colsout[outTCP],cex=0.8,pch=16)

#Ports
text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.07, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],7],offset = 0, cex = 0.7)
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.43, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],7],offset = 0, cex = 0.7)

#Duration

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.16, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.34, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Bytes

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.3, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.2, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Pakets

text(Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0+0.4, Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpout[Outflows[,3]=="UDP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])
text(Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1]*0-0.1, Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],1],
     labels = Outflows[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpout[Outflows[,3]=="TCP"&Outflows[,1]>=window[1]&Outflows[,1]<=window[2]])

#Inflows ##################

plot(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0,Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     col=colsin[inUDP],ylim=rev(window),pch=16,cex=0.8,xlim=c(-0.6,0.5),axes=FALSE,frame.plot=TRUE,
     main="Inflows 4: BBC",ylab=" " ,xlab=" ")
axis(side = 2, at = yax)
points(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.5,Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
       col=colsin[inTCP],cex=0.8,pch=16)

#Ports
text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.07, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],5],offset = 0, cex = 0.7)
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.43, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],5],offset = 0, cex = 0.7)

#Duration

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.16, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.34, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],2],offset = 0, cex = 0.7,col=coldin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

#Bytes

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.3, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.2, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],9],offset = 0, cex = 0.7,col=colbin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

#Pakets

text(Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0+0.4, Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpin[Inflows[,3]=="UDP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])
text(Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1]*0-0.1, Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],1],
     labels = Inflows[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2],8],offset = 0, cex = 0.7,col=colpin[Inflows[,3]=="TCP"&Inflows[,1]>=window[1]&Inflows[,1]<=window[2]])

```
